### 2013-07-06 latex/SupportingText.tex
Updated tables except angles

\begin{center}
\scriptsize
\begin{tabular}{lccccccccc}
 & \multicolumn{4}{c}{Empirical} &&\multicolumn{4}{c}{Theoretical}\\\cline{2-5}\cline{7-10}\\[-1.6ex]
Residue          & ALL & GENEROUS & ALLOWED & CORE & & ALL & GENEROUS & ALLOWED & CORE\\
\hline Alanine   & $121$ & $121$ & $121$ & $121$ & & $138$ & $132$ & $129$ & $128$\\
Arginine         & $265$ & $265$ & $265$ & $265$ & & $285$ & $280$ & $274$ & $274$\\
Asparagine       & $187$ & $187$ & $187$ & $187$ & & $204$ & $199$ & $195$ & $193$\\
Aspartate        & $187$ & $187$ & $187$ & $187$ & & $204$ & $197$ & $193$ & $192$\\
Cysteine         & $148$ & $148$ & $148$ & $133$ & & $169$ & $167$ & $167$ & $157$\\
Glutamate        & $214$ & $214$ & $214$ & $214$ & & $233$ & $227$ & $223$ & $222$\\
Glutamine        & $214$ & $214$ & $214$ & $214$ & & $234$ & $228$ & $225$ & $224$\\
Glycine          & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & & $114$ & $109$ & $104$ & $104$\\
Histidine        & $216$ & $216$ & $216$ & $216$ & & $213$ & $209$ & $209$ & $209$\\
Isoleucine       & $195$ & $195$ & $195$ & $195$ & & $208$ & $201$ & $197$ & $196$\\
Leucine          & $191$ & $191$ & $191$ & $191$ & & $211$ & $205$ & $201$ & $199$\\
Lysine           & $230$ & $230$ & $230$ & $229$ & & $246$ & $240$ & $236$ & $235$\\
Methionine       & $203$ & $203$ & $203$ & $203$ & & $227$ & $226$ & $224$ & $218$\\
Phenylalanine    & $228$ & $228$ & $228$ & $226$ & & $251$ & $244$ & $240$ & $236$\\
Proline          & $154$ & $154$ & $154$ & $154$ & & $166$ & $164$ & $159$ & $157$\\
Serine           & $143$ & $143$ & $143$ & $143$ & & $161$ & $158$ & $155$ & $150$\\
Threonine        & $163$ & $163$ & $163$ & $161$ & & $182$ & $176$ & $172$ & $171$\\
Tryptophan       & $264$ & $264$ & $264$ & $262$ & & $295$ & $293$ & $285$ & $282$\\
Tyrosine         & $255$ & $255$ & $255$ & $255$ & & $274$ & $266$ & $263$ & $262$\\
Valine           & $166$ & $166$ & $165$ & $165$ & & $184$ & $177$ & $174$ & $173$\\
\hline
\end{tabular}
\end{center}

@@

\centerline{
\begin{tabular}{ccccc}
& Mean RSA & Mean RSA &  & \\ 
Amino Acid & (theor)$^\text{a}$ & (emp)$^\text{b}$ & 100\% buried$^\text{c}$& 95\% buried$^\text{d}$ \\ 
\hline Alanine & 0.796 & 0.782 & 0.228 & 0.399\\ 
Arginine & 0.651 & 0.639 & 0.0121 & 0.0749\\ 
Asparagine & 0.672 & 0.658 & 0.0451 & 0.146\\ 
Asparate & 0.646 & 0.634 & 0.0276 & 0.104\\ 
Cysteine & 0.911 & 0.899 & 0.287 & 0.576\\ 
Glutamine & 0.654 & 0.636 & 0.0289 & 0.109\\ 
Glutamate & 0.605 & 0.589 & 0.0183 & 0.0717\\ 
Glycine & 0.749 & 0.731 & 0.166 & 0.291\\ 
Histidine & 0.723 & 0.731 & 0.0532 & 0.188\\ 
Isoleucine & 0.876 & 0.875 & 0.247 & 0.516\\ 
Leucine & 0.861 & 0.853 & 0.213 & 0.486\\ 
Lysine & 0.565 & 0.554 & 0.00597 & 0.0283\\ 
Methionine & 0.856 & 0.841 & 0.217 & 0.484\\ 
Phenylalanine & 0.87 & 0.864 & 0.186 & 0.483\\ 
Proline & 0.669 & 0.658 & 0.0607 & 0.162\\ 
Serine & 0.744 & 0.722 & 0.105 & 0.241\\ 
Threonine & 0.742 & 0.728 & 0.0987 & 0.237\\ 
Tryptophan & 0.849 & 0.837 & 0.0979 & 0.368\\ 
Tyrosine & 0.818 & 0.813 & 0.0797 & 0.306\\ 
Valine & 0.864 & 0.857 & 0.25 & 0.494\\ 
\hline
\end{tabular}
}

>>>>

\begin{center}
\scriptsize
\begin{tabular}{lccccccccc}
 & \multicolumn{4}{c}{Empirical} &&\multicolumn{4}{c}{Theoretical}\\\cline{2-5}\cline{7-10}\\[-1.6ex]
Residue          & ALL & GENEROUS & ALLOWED & CORE & & ALL & GENEROUS & ALLOWED & CORE\\
\hline Alanine   & $121$ & $121$ & $121$ & $121$ & & $138$ & $132$ & $129$ & $128$\\
Arginine         & $265$ & $265$ & $265$ & $265$ & & $285$ & $280$ & $274$ & $274$\\
Asparagine       & $187$ & $187$ & $187$ & $187$ & & $204$ & $199$ & $195$ & $193$\\
Aspartate        & $187$ & $187$ & $187$ & $187$ & & $204$ & $197$ & $193$ & $192$\\
Cysteine         & $148$ & $148$ & $148$ & $133$ & & $169$ & $167$ & $167$ & $157$\\
Glutamate        & $214$ & $214$ & $214$ & $214$ & & $233$ & $227$ & $223$ & $222$\\
Glutamine        & $214$ & $214$ & $214$ & $214$ & & $234$ & $228$ & $225$ & $224$\\
Glycine          & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & $\phantom{0}97$ & & $114$ & $109$ & $104$ & $104$\\
Histidine        & $216$ & $216$ & $216$ & $216$ & & $231$ & $228$ & $224$ & $219$\\
Isoleucine       & $195$ & $195$ & $195$ & $195$ & & $208$ & $201$ & $197$ & $196$\\
Leucine          & $191$ & $191$ & $191$ & $191$ & & $211$ & $205$ & $201$ & $199$\\
Lysine           & $230$ & $230$ & $230$ & $229$ & & $246$ & $240$ & $236$ & $235$\\
Methionine       & $203$ & $203$ & $203$ & $203$ & & $227$ & $226$ & $224$ & $218$\\
Phenylalanine    & $228$ & $228$ & $228$ & $226$ & & $251$ & $244$ & $240$ & $236$\\
Proline          & $154$ & $154$ & $154$ & $154$ & & $166$ & $164$ & $159$ & $157$\\
Serine           & $143$ & $143$ & $143$ & $143$ & & $161$ & $158$ & $155$ & $150$\\
Threonine        & $163$ & $163$ & $163$ & $161$ & & $182$ & $176$ & $172$ & $171$\\
Tryptophan       & $264$ & $264$ & $264$ & $262$ & & $295$ & $293$ & $285$ & $282$\\
Tyrosine         & $255$ & $255$ & $255$ & $255$ & & $274$ & $266$ & $263$ & $262$\\
Valine           & $166$ & $166$ & $165$ & $165$ & & $184$ & $177$ & $174$ & $173$\\
\hline
\end{tabular}
\end{center}

@@

\centerline{
\begin{tabular}{ccccc}
& Mean RSA & Mean RSA &  & \\ 
Amino Acid & (theor)$^\text{a}$ & (emp)$^\text{b}$ & 100\% buried$^\text{c}$& 95\% buried$^\text{d}$ \\ 
\hline Alanine & 0.796 & 0.782 & 0.228 & 0.399\\ 
Arginine & 0.651 & 0.639 & 0.0121 & 0.0749\\ 
Asparagine & 0.672 & 0.658 & 0.0451 & 0.146\\ 
Asparate & 0.646 & 0.634 & 0.0276 & 0.104\\ 
Cysteine & 0.911 & 0.899 & 0.287 & 0.576\\ 
Glutamine & 0.654 & 0.636 & 0.0289 & 0.109\\ 
Glutamate & 0.605 & 0.589 & 0.0183 & 0.0717\\ 
Glycine & 0.749 & 0.731 & 0.166 & 0.291\\ 
Histidine & 0.741 & 0.731 & 0.0532 & 0.198\\ 
Isoleucine & 0.876 & 0.875 & 0.247 & 0.516\\ 
Leucine & 0.861 & 0.853 & 0.213 & 0.486\\ 
Lysine & 0.565 & 0.554 & 0.00597 & 0.0283\\ 
Methionine & 0.856 & 0.841 & 0.217 & 0.484\\ 
Phenylalanine & 0.87 & 0.864 & 0.186 & 0.483\\ 
Proline & 0.669 & 0.658 & 0.0607 & 0.162\\ 
Serine & 0.744 & 0.722 & 0.105 & 0.241\\ 
Threonine & 0.742 & 0.728 & 0.0987 & 0.237\\ 
Tryptophan & 0.849 & 0.837 & 0.0979 & 0.368\\ 
Tyrosine & 0.818 & 0.813 & 0.0797 & 0.306\\ 
Valine & 0.864 & 0.857 & 0.25 & 0.494\\ 
\hline
\end{tabular}
}

### 2013-07-06 latex/paper-PLOS_ONE-revised.tex
Updated tables except angles

\begin{center}
\begin{tabular}{lcccc}
Residue & Theoretical & Empirical & Miller \emph{et al.} (1987) & Rose \emph{et al.} (1985) \\
\hline Alanine & 129.0 & 121.0 & 113.0 & 118.1 \\
Arginine        & 274.0 & 265.0 & 241.0 & 256.0 \\
Asparagine    & 195.0 & 187.0 & 158.0 & 165.5 \\
Aspartate      & 193.0 & 187.0 & 151.0 & 158.7 \\
Cysteine        & 167.0 & 148.0 & 140.0 & 146.1 \\
Glutamate     & 223.0 & 214.0 & 183.0 & 186.2 \\
Glutamine      & 225.0 & 214.0 & 189.0 & 193.2  \\
Glycine          & 104.0 & 97.0 & 85.0 & 88.1  \\
Histidine        & 209.0 & 216.0 & 194.0 & 202.5  \\
Isoleucine     & 197.0 & 195.0 & 182.0 & 181.0  \\
Leucine         & 201.0 & 191.0 & 180.0 & 193.1  \\
Lysine           & 236.0 & 230.0 & 211.0 & 225.8  \\
Methionine   & 224.0 & 203.0 & 204.0 & 203.4  \\
Phenylalanine  & 240.0 & 228.0 & 218.0 & 222.8  \\
Proline & 159.0 & 154.0& 143.0 & 146.8  \\
Serine          & 155.0 & 143.0 & 122.0 & 129.8  \\
Threonine          & 172.0 & 163.0 & 146.0 & 152.5  \\
Tryptophan          & 285.0 & 264.0 & 259.0 & 266.3  \\
Tyrosine          & 263.0 & 255.0 & 229.0 & 236.8 \\
Valine          & 174.0 & 165.0 & 160.0 & 164.5  \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[H]
\caption{\label{tab:Corr}Absolute value of correlation coefficients $r$ between empirically derived and experimentally derived hydrophobicity scales. The largest significant correlation in each row is highlighted in bold.}
\begin{center}
\footnotesize
\begin{tabular}{lccccc}
 & \multicolumn{5}{c}{Empirical scale} \\ \cline{2-6}\\[-2ex]
Experimental scale & Mean RSA (Rose)$^\text{a}$ & Mean RSA (theor)$^\text{b}$ & Mean RSA (emp)$^\text{c}$ & 100\% buried$^\text{d}$ & 95\% buried$^\text{e}$\\
\hline
Wolfenden \emph{et al.}$^\text{f}$ & 0.614 & 0.691 & 0.681 & \textbf{0.827} & 0.775 \\
Kyte \& Doolittle$^\text{g}$ & 0.841 & 0.885 & 0.881 & \textbf{0.953} & 0.948 \\
Radzicka \& Wolfenden$^\text{h}$ & 0.804 & 0.855 & 0.851 & 0.844 & \textbf{0.888} \\
Moon \& Fleming$^\text{i}$ & 0.704 & 0.761 & 0.752 & 0.678 & \bf{0.768} \\
Fauchere \& Pliska$^\text{l}$ & 0.904 & 0.907 & \textbf{0.910} & 0.734 & 0.878 \\
Wimley \emph{et al.}$^\text{m}$ & 0.430$^\dagger$ & 0.464 & \textbf{0.473} & 0.323$^\dagger$ & 0.416$^\dagger$ \\
MacCallum \emph{et al.}$^\text{k}$ & 0.318$^\dagger$ & 0.265$^\dagger$ & 0.285$^\dagger$ & 0.116$^\dagger$ & 0.227$^\dagger$ \\
\hline
\end{tabular}
\end{center}
{\footnotesize
\begin{raggedright}
$^\text{a}$Mean RSA of residues in protein structures, as calculated by Rose \emph{et al.}~\cite{Rose1985}.\\
$^\text{b}$Mean RSA of residues in protein structures, as given in column 2 of Table~\ref{tab:hydro_scales}.\\ 
$^\text{c}$Mean RSA of residues in protein structures, as given in column 3 of Table~\ref{tab:hydro_scales}.\\
$^\text{d}$Fraction of 100\% buried residues, as given in column 4 of Table~\ref{tab:hydro_scales}.\\
$^\text{e}$Fraction of 95\% buried residues, as given in column 5 of Table~\ref{tab:hydro_scales}.\\
$^\text{f}$Transfer energy from vapor to water~\cite{Wolfenden1981}.\\
$^\text{g}$Hybrid scale based on transfer energy from vapor to water and on the percentages of 95\% and 100\% buried residues in protein structures~\cite{Kyte1981}.\\
$^\text{h}$Transfer energy from cyclohexane to water~\cite{Radzicka1988}.\\
$^\text{i}$$\Delta\Delta G$ between the folded and unfolded state of a mutated membrane-inserted protein, outer membrane phospholipase~A~\cite{Moon2011}. \\
$^\text{k}$Transfer energy calculated from molecular-dynamic simulations of side-chain analogs within a bilayer~\cite{MacCallum2007}.\\
$^\text{l}$Transfer energy between octanol and water~\cite{Fauchere1983}.\\
$^\text{m}$Transfer energy of pentapeptides between octanol and water~\cite{Wimley1996}.\\
$^\dagger$Correlation not statistically significant; all other correlations are significant at $\alpha=0.05$.\\
\end{raggedright}
}
\end{table}

>>>>

\begin{center}
\begin{tabular}{lcccc}
Residue & Theoretical & Empirical & Miller \emph{et al.} (1987) & Rose \emph{et al.} (1985) \\
\hline Alanine & 129.0 & 121.0 & 113.0 & 118.1 \\
Arginine        & 274.0 & 265.0 & 241.0 & 256.0 \\
Asparagine    & 195.0 & 187.0 & 158.0 & 165.5 \\
Aspartate      & 193.0 & 187.0 & 151.0 & 158.7 \\
Cysteine        & 167.0 & 148.0 & 140.0 & 146.1 \\
Glutamate     & 223.0 & 214.0 & 183.0 & 186.2 \\
Glutamine      & 225.0 & 214.0 & 189.0 & 193.2  \\
Glycine          & 104.0 & 97.0 & 85.0 & 88.1  \\
Histidine        & 224.0 & 216.0 & 194.0 & 202.5  \\
Isoleucine     & 197.0 & 195.0 & 182.0 & 181.0  \\
Leucine         & 201.0 & 191.0 & 180.0 & 193.1  \\
Lysine           & 236.0 & 230.0 & 211.0 & 225.8  \\
Methionine   & 224.0 & 203.0 & 204.0 & 203.4  \\
Phenylalanine  & 240.0 & 228.0 & 218.0 & 222.8  \\
Proline & 159.0 & 154.0& 143.0 & 146.8  \\
Serine          & 155.0 & 143.0 & 122.0 & 129.8  \\
Threonine          & 172.0 & 163.0 & 146.0 & 152.5  \\
Tryptophan          & 285.0 & 264.0 & 259.0 & 266.3  \\
Tyrosine          & 263.0 & 255.0 & 229.0 & 236.8 \\
Valine          & 174.0 & 165.0 & 160.0 & 164.5  \\
\hline
\end{tabular}
\end{center}
\end{table}

\begin{table}[H]
\caption{\label{tab:Corr}Absolute value of correlation coefficients $r$ between empirically derived and experimentally derived hydrophobicity scales. The largest significant correlation in each row is highlighted in bold.}
\begin{center}
\footnotesize
\begin{tabular}{lccccc}
 & \multicolumn{5}{c}{Empirical scale} \\ \cline{2-6}\\[-2ex]
Experimental scale & Mean RSA (Rose)$^\text{a}$ & Mean RSA (theor)$^\text{b}$ & Mean RSA (emp)$^\text{c}$ & 100\% buried$^\text{d}$ & 95\% buried$^\text{e}$\\
\hline
Wolfenden \emph{et al.}$^\text{f}$ & 0.614 & 0.681 & 0.681 & \textbf{0.827} & 0.774 \\
Kyte \& Doolittle$^\text{g}$ & 0.841 & 0.879 & 0.881 & \textbf{0.953} & 0.948 \\
Radzicka \& Wolfenden$^\text{h}$ & 0.852 & 0.855 & 0.851 & 0.844 & \textbf{0.888} \\
Moon \& Fleming$^\text{i}$ & 0.704 & 0.748 & 0.752 & 0.678 & \bf{0.764} \\
Fauchere \& Pliska$^\text{l}$ & 0.904 & 0.906 & \textbf{0.910} & 0.734 & 0.878 \\
Wimley \emph{et al.}$^\text{m}$ & 0.463$^\dagger$ & 0.464 & \textbf{0.473} & 0.323$^\dagger$ & 0.417$^\dagger$ \\
MacCallum \emph{et al.}$^\text{k}$ & 0.27$^\dagger$ & 0.265$^\dagger$ & 0.285$^\dagger$ & 0.116$^\dagger$ & 0.227$^\dagger$ \\
\hline
\end{tabular}
\end{center}
{\footnotesize
\begin{raggedright}
$^\text{a}$Mean RSA of residues in protein structures, as calculated by Rose \emph{et al.}~\cite{Rose1985}.\\
$^\text{b}$Mean RSA of residues in protein structures, as given in column 2 of Table~\ref{tab:hydro_scales}.\\ 
$^\text{c}$Mean RSA of residues in protein structures, as given in column 3 of Table~\ref{tab:hydro_scales}.\\
$^\text{d}$Fraction of 100\% buried residues, as given in column 4 of Table~\ref{tab:hydro_scales}.\\
$^\text{e}$Fraction of 95\% buried residues, as given in column 5 of Table~\ref{tab:hydro_scales}.\\
$^\text{f}$Transfer energy from vapor to water~\cite{Wolfenden1981}.\\
$^\text{g}$Hybrid scale based on transfer energy from vapor to water and on the percentages of 95\% and 100\% buried residues in protein structures~\cite{Kyte1981}.\\
$^\text{h}$Transfer energy from cyclohexane to water~\cite{Radzicka1988}.\\
$^\text{i}$$\Delta\Delta G$ between the folded and unfolded state of a mutated membrane-inserted protein, outer membrane phospholipase~A~\cite{Moon2011}. \\
$^\text{k}$Transfer energy calculated from molecular-dynamic simulations of side-chain analogs within a bilayer~\cite{MacCallum2007}.\\
$^\text{l}$Transfer energy between octanol and water~\cite{Fauchere1983}.\\
$^\text{m}$Transfer energy of pentapeptides between octanol and water~\cite{Wimley1996}.\\
$^\dagger$Correlation not statistically significant; all other correlations are significant at $\alpha=0.05$.\\
\end{raggedright}
}
\end{table}
